Performance of Jellyfish Search Optimiser on Projection Pursuit Problems

### 2024-02-05 optim.qmd
add metaheuristics reference

The artificial jellyfish search (JS) algorithm [@chou_novel_2021] is a swarm-based metaheuristic optimisation algorithm inspired by the search behaviour of jellyfish in the ocean. It is one of the newest swarm intelligence algorithms, which was shown to have stronger search ability and faster convergence with few algorithmic parameters compared to classic optimization methods [@chou_novel_2021]-[@chou_recent_2022].

>>>>

The artificial jellyfish search (JS) algorithm [@chou_novel_2021] is a swarm-based metaheuristic optimisation algorithm inspired by the search behaviour of jellyfish in the ocean. It is one of the newest swarm intelligence algorithms [@rajwar_exhaustive_2023], which was shown to have stronger search ability and faster convergence with few algorithmic parameters compared to classic optimization methods [@chou_novel_2021]-[@chou_recent_2022].

### 2024-02-05 optim.tex
add metaheuristics reference

\begin{keyword}
    projection pursuit \sep optimization \sep 
    jellyfish optimiser
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, boxrule=0pt, sharp corners, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

@@

The artificial jellyfish search (JS) algorithm \citep{chou_novel_2021}
is a swarm-based metaheuristic optimisation algorithm inspired by the
search behaviour of jellyfish in the ocean. It is one of the newest
swarm intelligence algorithms, which was shown to have stronger search
ability and faster convergence with few algorithmic parameters compared
to classic optimization methods
\citep{chou_novel_2021}-\citep{chou_recent_2022}.

>>>>

\begin{keyword}
    projection pursuit \sep optimization \sep 
    jellyfish optimiser
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

The artificial jellyfish search (JS) algorithm \citep{chou_novel_2021}
is a swarm-based metaheuristic optimisation algorithm inspired by the
search behaviour of jellyfish in the ocean. It is one of the newest
swarm intelligence algorithms \citep{rajwar_exhaustive_2023}, which was
shown to have stronger search ability and faster convergence with few
algorithmic parameters compared to classic optimization methods
\citep{chou_novel_2021}-\citep{chou_recent_2022}.
